\Large \bf Dynamic Program Dialysis with Lya

### 2019-12-23 paper/draft.tex
Update related work

@@

Existing dynamic analysis frameworks can be classified either as coarse- or fine-grained.
The former analyze interactions at the boundaries of entire components, whereas the latter associate metadata at the level of individual instructions or objects.
We compare \sys to previously proposed systems in both categories, then contrast the two categories' overall characteristics.

\heading{Heavyweight instrumentation}
There is a series of heavyweight dynamic analysis frameworks.
Popular frameworks include
  Valgrind~\cite{valgrind} and Pin~\cite{pin} for native programs,
  DiSL~\cite{disl} and RoadRunner~\cite{roadrunner} for JVM byte code,
  Jalangi~\cite{jalangi} for JavaScript programs, and,
  most recently, Wasabi~\cite{wasabi} for Web-Assembly.

The approach advocated by \sys is to throw a quick-and-easy analysis at the module boundaries

Jalangi is the most relevant of these frameworks, and served as an inspiration

\heading{Dynamic Analysis for WebAssembly}
Related to JavaScript is WebAssembly, a standardized subset of JavaScript target ideal as a compilation target.
Two techniques modify V8

Wasabi is a framework for dynamic analysis of WebAssembly.
Similar to \sys, it succeeds at lowering the effort required to write analyses, 
and provides hooks for observation rather than manipulation
Contrary to \sys, Wasabi instruments binaries statically, \ie ahead-of-time, and aims on heavyweight instrumentation.

; even more similarly, it allows expressing analyses in JavaScript.
Prior work has modified

Some citations to ensure we can see them~\cite{javascript1, javascript2, javascript3}.

\heading{Dynamic Instrumentation}
Dialysis is related to dynamic binary instrumentation frameworks that wrap parts of the program to extract information.
Many such frameworks translate basic blocks of the program just before their execution;
  \sys starts with a phase that wraps (equivalent to instrumenting) a library during import, adding a small overhead at the loading time of each library.
The overhead of this phase is only a small fraction of the time required to locate and load the module from disk.

\heading{Program Transformations}
% Add our work
Module dialysis builds on aspect-oriented programming (AOP), a programming model that maps program points to actions to be taken at these points~\cite{aop}.
Both approaches lower complexity by mapping multiple points across the program to the same actions, but dialysis does not alter the program's control flow.
Moreover, AOP works on languages that were already designed to support it, whereas module dialysis was explicitly designed to bolt onto existing languages and environments.

More generally AOP is related to metaobjects~\cite{metaobject}, objects that manipulate object structure and which enable a program to access to its own internal structure, including rewriting itself as it executes.
They are examples of runtime reflection, of which \sys makes extensive use to traverse, understand, wrap, and rewrite interfaces.
With \sys, however, developers do not need to provide their own metaobjects.
% self element

\heading{Fracture and Recombination}
Module dialysis draws inspiration directly from program fracture and recombination (PFR)~\cite{fracture1, fracture3}, a line of work less tied to program analysis and more towards program synthesis and automated patch generation.
PFR breaks up multiple programs into multiple components (called shards) with the goal of exchanging functionality between donor-donee pairs of programs.
Module dialysis operates on single programs, avoids breaking semantics, and leverages the existence of components with (mostly) explicit boundaries, in the guise of libraries or modules.

>>>>

\subsection{When to Use Dialysis}
\label{principles}
Dynamic analysis is a general analysis technique that discovering facts about programs;
  dialysis can be thought as a specif
While full-fledged dynamic analysis can provide full visibility into , it may result in higher performance overheads and developer effort.

Dialysis deconstructs programs only at the library boundaries, at a granularity well-suited for several tasks.
By viewing the program's surrounding environment as libraries---which is the case in all high-level programming languages---dialysis can expand its coverage to the operating system, file system, network and other ``ambient'' services.

Another use is in the existence of multi-language applications---wrappers and FFI.

@@

In this section, we compare \sys to previously proposed systems in several categories.
For a comparison between dialysis and dynamic analysis, we refer the reader to the previous section~\sx{principles}.

\heading{Dynamic Analysis Systems}
There are several dynamic analysis frameworks for JavaScript~\cite{javascript1, javascript2, javascript3, mugshot, jalangi}.
The two most popular, Jalangi~\cite{jalangi} and Mugshot~\cite{mugshot}, are fine-grained code-level instrumentation tools.
On top of analysis, their heavy instrumentation is powerful enough to record and replay entire program executions.
This power comes at a significant performance cost---typically 2--3 order-of-magnitude slowdown---as they need to virtualize the entire execution environment:
  source-code-level rewriting every expression corresponding to a profiling event in the original program needs is resolves to a profiling function call.
They are also not embeddable in existing applications in a runtime-agnostic manner.
These features are contrary to \sys, which leverages fairly basic programming-language techniques such as variable shadowing and context transformation during library loading to insert analysis hooks completely transparently to the runtime environment.

NodeProf~\cite{javascript3} is a fine-grained dynamic analysis implemented using Truffle~\cite{} and running on top of Graal.js [28], a Node.js-compatible runtime.
NodeProf takes a different approach than code-level instrumentation, statically instrumenting the AST, which makes it easier to maintain compared to source changes.
Similar to \sys, NodeProf 
is not tied to the source code, has significantly lower overheads, and can be toggled on/off during program execution.
Requires AST extraction and manipulation to build, which is not available in many languages % it is an additional requirement
and is in conflict with many dynamic features. 
It stands at a different point in the design space---more powerful analysis, but with significantly more effort:
  assumes knowledge of the internal Graal and Truffle APIs and requires recompilation of the Java hooks.

Similar to NodeProf, \sys

Aran~\cite{javascript1} is presented in a poster to

JSConTest2~\cite{javascript2} is a dynamic \emph{access} analysis framework, similar to \sys's analysis \fixme{A2}, build around proxies.
It allows users to write 
It illustrates the need for a general-purpose framework such as \sys, as many of JSConTest2's access permission contracts are 
Our evaluation shows that this analysis (and others) can be implemented on top of \sys with significantly less effort.

\heading{Dynamic Analysis for WebAssembly}
Related to JavaScript is WebAssembly, a standardized subset of JavaScript target, designed to serve as a compilation target.
The first dynamic analysis framework for WebAssembly, Wasabi~\cite{wasabi}, shares some of the same goals with \sys---\eg lowering the effort required to write analyses, and providing hooks for observation rather than manipulation.
Wasabi is also programmable in JavaScript (which, however, is not its target language), a similarity to \sys that is mostly accidental:
  Wasabi needs to be provide a high-level analysis scripting interface and chose JavaScript;
  whereas our explicit goal is to write analysis in the same language as the program~\sx{goals}---that is, dialysis implemented for Python would be using Python abstractions.
Contrary to \sys, Wasabi instruments binaries statically, \ie ahead-of-time, and aims on heavyweight instrumentation.

\heading{Dynamic Instrumentation}
Dialysis is related to dynamic instrumentation frameworks~\cite{pin, valgrind} that wrap incrementally parts of the program to extract information.
Pin~\cite{pin} and Valgrind~\cite{valgrind} translate basic blocks of the program just before their execution;
  \sys starts by wrapping a library during import, adding a small overhead on its loading time.
This overhead is only a small fraction of the time required to locate and load the module from disk.
However, these systems operate at a much lower level (binary) than \sys, and are not available to high-level runtime environments as a pluggable library.

DiSL~\cite{disl} and RoadRunner~\cite{roadrunner} are systems for instrumenting JVM byte code.
These too work at a lower level than \sys,

\heading{Program Transformations}
% Add our work
Module dialysis builds on aspect-oriented programming (AOP), a programming model where program points map to actions taken at these points~\cite{aop}.
Both approaches lower complexity by mapping multiple points across the program to the same actions, but dialysis does not alter the program's control flow.
Moreover, AOP works on languages that were already designed to support it, whereas module dialysis is explicitly designed to bolt onto existing languages.

More generally AOP is related to metaobjects~\cite{metaobject}, objects that manipulate object structure, and which enable a program to access to its own internal structure, including rewriting itself as it executes.
While \sys makes extensive use of metaobjects to traverse, understand, wrap, and rewrite interfaces, it shields developers from building the required metaobject infrastructure.
% self element

\heading{Fracture and Recombination}
Dialysis draws inspiration directly from program fracture and recombination (PFR)~\cite{fracture1, fracture3}, a line of work less tied to program analysis and more towards program synthesis and automated patch generation.
PFR breaks up multiple programs into many components with the goal of exchanging functionality between donor-donee pairs of programs.
Contrary to PFR, dialysis operates on single programs, avoids breaking semantics, and leverages the existence of components with (mostly) explicit boundaries in the guise of libraries or modules.
